### 2009-04-30 poc1/apresentacao_monografia/apresentacao_monografia.tex

% This text is proprietary.
% It's a part of presentation made by myself.
% It may not used commercial.
% The noncommercial use such as private and study is free
% May 2007
% Author: Sascha Frank 
% University Freiburg 
% www.informatik.uni-freiburg.de/~frank/
%
% 
\documentclass{beamer}
\usepackage[latin1]{inputenc}
\usepackage[brazil]{babel}

%Temas
\usetheme[compress]{Dresden}
%\useoutertheme[subsection=false]{smoothbars}
%\useinnertheme[shadow]{rounded}
\useinnertheme{rectangles}

\makeatletter
\beamer@theme@subsectionfalse
\makeatother

\usebackgroundtemplate{\includegraphics[width=\paperwidth]{img/fundo}}

\begin{document}
\title[Geração Procedural de Terrenos em Tempo-Real]{Desenvolvimento de um Arcabouço para a Geração Procedural e Visualização de Terrenos em Tempo-Real}
\author[Fábio Miranda - Apresentação final - POC I]{Fábio Markus Nunes Miranda\\Orientador: Prof. Luiz Chaimowicz\\Co-Orientador: Carlúcio Cordeiro}
\institute[Universidade Federal de Minas Gerais]{Departamento de Ciência da Computação\\Universidade Federal de Minas Gerais}
\date[\today]{Apresentação final - POC I}

\begin{frame}
\titlepage
\end{frame}

\AtBeginSection[]
{
\begin{frame}
\frametitle{Sumário}
\setcounter{tocdepth}{1}
\tableofcontents[currentsection]
\setcounter{tocdepth}{2}
\end{frame}
}

\include{motivacao}
\include{metodologia}
\include{proposta}
\include{resultados}
\include{conclusao}

\section{Bibliografia}
\begin{tiny}
\nocite{*}
\bibliographystyle{unsrt}
\bibliography{apresentacao_monografia}
\end{tiny}

\begin{frame}
\Large Dúvidas?
\end{frame}

\end{document}