### 2009-04-30 poc1/monografia/tabela_tempos.tex

\begin{table}[H]
	\begin{center}
		\begin{tabular}{|c|c|c|c|c|c|c|}
			\hline
			 - & \multicolumn{3}{|c|}{FillHeightMap} & \multicolumn{3}{|c|}{CopyHeightMap} \\
			\hline
			\emph{Octaves} & \scriptsize Mín. & \scriptsize Máx. & \scriptsize Média & \scriptsize Mín. & \scriptsize Máx. & \scriptsize Média \\
			\hline
			4 & 0,0410248 & 0,0536568 & 0,0443777 & 0,0737747 & 0,0866761 & 0,0782942 \\
			\hline
			16 & 0,1644840 & 0,2593410 & 0,1698030 & 0,0710867 & 0,0865546 & 0,0734247 \\
			\hline
			32 & 0,3315010 & 0,4503400 & 0,3405685 & 0,0708154 & 0,0778093 & 0,0730120 \\
			\hline

		\end{tabular}
		\caption{Tempos da geração dos terrenos (em segundos)}
		\label{tabela:geracao1}
	\end{center}
\end{table}

\begin{table}[H]
	\begin{center}
		\begin{tabular}{|c|c|c|c|c|c|c|}
			\hline
			 - & \multicolumn{3}{|c|}{BuildVBOs} & \multicolumn{3}{|c|}{Total}  \\
			\hline
			\emph{Octaves} & \scriptsize Mín. & \scriptsize Máx. & \scriptsize Média & \scriptsize Mín. & \scriptsize Máx. & \scriptsize Média \\
			\hline
			4 & 0,0078359 & 0,0161562 & 0,0107964 & 0,1264320 & 0,1498800 & 0,1336476 \\
			\hline
			16 & 0,0081773 & 0,0407795 & 0,0114127 & 0,2469740 & 0,3459500 & 0,2550180 \\
			\hline
			32 & 0,0075448 & 0,0129804 & 0,0093645 & 0,4121210 & 0,5310980 & 0,4231183 \\
			\hline
		\end{tabular}
		\caption{Tempos da geração dos terrenos (em segundos)}
		\label{tabela:geracao2}
	\end{center}
\end{table}