### 2009-06-22 poc2/monografia/epigrafe.tex

%  Epígrafe - é uma citação pertinente ao seu trabalho
%  ou que represente o seu modo de pensar.
%  Resumindo, coloque uma frase que o(a) agrade.

\pretextualchapter{}
\vspace{8cm}
\begin{flushright}
\textnormal{```Fractal geometry will make you see everything differently. \\
	 You risk the loss of your childhood vision of clouds, forests,\\
	 flowers, galaxies, leaves, feathers, rocks, mountains,\\
	 torrents of water, carpets, bricks, and much else besides.\\
	 Never again will your interpretation of these things be quite the same.'' \\
	\bfseries Michael F. Barnsley}
\end{flushright}