### 2009-06-24 poc2/monografia/abstract.tex

\begin{abstract}

With the increasing demand for 3D models in areas such as games, the procedural content generation is becoming increasingly popular, in order to reduce costs and development time. With procedural techniques, it is possible to create a large number of models modifying a few parameters on the algorithms responsable for the generation. This work plans to utilizy the power of the modern video cards (\emph{GPU}) to generate infinit terrains. A comparative between \emph{GPU} generation and \emph{CPU} is made, in order to avaliate the performance of the two different architectures.

    \textbf{Keywords}: Procedural content generation, terrain, gpu.
\end{abstract}