### 2009-07-06 paper/conceitosBasicos.tex
paper

\section{Conceitos básicos}

\subsection{Ruído Perlin}

\subsection{Fractais}

\subsection{Ridged Multifractal Noise}