### 2009-07-07 paper/trabalhosFuturosConclusao.tex

\section{Conclusão e Trabalhos Futuros}
\label{conclusao}